Moving Towards Reproducible and Programmatic Generation of Neuroimaging Visualizations

### 2022-09-05 manuscript.Rmd
title update

---
title: Moving Towards Reproducible and Programmatic Generation of Neuroimaging Visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Elvisha Dhamala
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Avram Holmes
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
keywords:
  - Neuroimaging visualization
  - Reproducibility 
  - Programmatic figures
  - Open Science
  - R
  - Python
  - Brain Visualization
abstract: Neuroimaging visualization forms the centerpiece of interpretation and communication of scientific results, as well as data quality control. Often, these images and figures are produced by manually changing settings on Graphical User Interfaces (GUI). There now exist many well-documented code-based brain visualization tools that allow users to programmatically generate publication-ready figures directly within R, Python and MATLAB environments. Compared to figures generated using GUIs, programmatic figures are more replicable, flexible, interactive, and integrated with the scientific process. Here we outline the advantages of using programmatic neuroimaging visualization tools, provide a list of avalible tools across programming environments and include examples of voxel, vertex, region-of-interest and edge-level visualizations.

>>>>

---
title: Moving Towards Reproducible and Programmatic Generation of Neuroimaging Visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Elvisha Dhamala
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Avram Holmes
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
keywords:
  - Neuroimaging visualization
  - Reproducibility 
  - Programmatic figures
  - Open Science
  - R
  - Python
  - Brain Visualization
abstract: Neuroimaging visualization forms the centerpiece of interpretation and communication of scientific results, as well as data quality control. Often, these images and figures are produced by manually changing settings on Graphical User Interfaces (GUI). There now exist many well-documented code-based brain visualization tools that allow users to programmatically generate publication-ready figures directly within R, Python and MATLAB environments. Compared to figures generated using GUIs, programmatic figures are more replicable, flexible, interactive, and integrated with the scientific process. Here we outline the advantages of using programmatic neuroimaging visualization tools, provide a list of available tools across programming environments and include examples of voxel, vertex, region-of-interest and edge-level visualizations.
